---
title: "Clean Raw Data"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

librarian::shelf("freeR", "glue", "googledrive", "here", "janitor", "lubridate", "readxl", "tidyverse")

options(scipen=999)

dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/Palmyra_DataTransfer_EDI_Project"
```

## Read in the Data from Google Drive 

To do this step, you need to have Google Drive installed on your computer so that you can access Google Drive files using Google File Stream 

```{r}

fish_data <- read_csv(glue("{dir_gdrive}/Data/Caselle Scripps Fish Data/casell_sandin_fish_clean/PARC_FishSurvey_Data_v1.csv")) %>% 
  clean_names()

site_list <- read_csv(glue("{dir_gdrive}/Data/Caselle Scripps Fish Data/casell_sandin_fish_clean/PANWR_PARC_SITELIST_v1.csv")) %>% 
  clean_names()

# taxonomy <- read_excel(glue("{dir_gdrive}/DATA_RAW/Scripps_Caselle_Fish_Data/PARC_FISH_Taxonomy_Table_Temporary.xlsx")) %>% 
#   clean_names()



```


## Explore the Data 

### Fish Data 

```{r}
str(fish_data)

sort(unique(fish_data$project))
class(fish_data$project)
sort(unique(fish_data$reef))
sort(unique(fish_data$date))
class(fish_data$date)
sort(unique(fish_data$station_clean))
class(fish_data$station_clean)
sort(unique(fish_data$transect))
class(fish_data$transect)
sort(unique(fish_data$depth_zn))
sort(unique(fish_data$species))
class(fish_data$diver_tx_depthzn)

```


#### Fish Data Changes Required 

- Remove the diver_tx_depth variable because all of the information is already there and it is cause a very large categorical variables table in the EML

##### Clean the Data 

```{r}
fish_data_clean <- fish_data %>% 
  mutate(project = as.factor(project), 
         transect = as.factor(transect), 
         diver_tx_depthzn = as.character(diver_tx_depthzn)) %>% 
  select(-diver_tx_depthzn)


write_csv(fish_data_clean, glue("{dir_gdrive}/Data/Caselle Scripps Fish Data/casell_sandin_fish_clean/clean_data/scripps_caselle_fish_data.csv"))

```


### Site List Data 

```{r}
str(site_list)

sort(unique(site_list$habitat_zone))
sort(unique(site_list$lat_dd))
class(site_list$lat_dd)
class(site_list$long_dd)
sort(unique(site_list$activity))
class(site_list$activity)

```


#### Site List Changes 

- Move the `station_clean` to the first column because that is the reference to the other table 
- Make `lat_dd` & `long_dd` numeric 
- make  `activity` categorical 

##### Clean the Data 

```{r}

sort(unique(site_list$lat_dd))

site_list_clean <- site_list %>% 
  select(station_clean, everything())

site_list_clean[site_list_clean == "NA"] <- NA

site_list_clean <- site_list_clean %>% 
  mutate(lat_dd = as.numeric(lat_dd), 
         long_dd = as.numeric(long_dd), 
         activity = as.factor(activity)) %>% 
  filter(activity == "FISH") %>% 
  select(-activity)

write_csv(site_list_clean, glue("{dir_gdrive}/Data/Caselle Scripps Fish Data/casell_sandin_fish_clean/clean_data/scripps_caselle_site_list.csv"))
```


<!-- ### Taxonomy Table  -->

<!-- ```{r} -->
<!-- str(taxonomy) -->
<!-- sort(unique(taxonomy$trophic_group)) -->
<!-- class(taxonomy$trophic_group) -->
<!-- sort(unique(taxonomy$length_type)) -->
<!-- sort(unique(taxonomy$species)) -->

<!-- class(taxonomy$family) -->
<!-- ``` -->

<!-- #### Taxonomy Table Changes  -->

<!-- - Move  `species` to the first column because it is the link to the other table. -->
<!-- - Make `trophic_group` categorical  -->
<!-- - Make  `length_type` categorical and change ? to NA  -->

<!-- ##### Clean the Data  -->

<!-- ```{r} -->
<!-- taxonomy_clean <- taxonomy %>%  -->
<!--   select(species, everything()) -->

<!-- taxonomy_clean[taxonomy_clean == "?" | taxonomy_clean == "??" ] <- NA -->

<!-- taxonomy_clean <- taxonomy_clean %>%  -->
<!--   mutate(length_type = as.factor(length_type),  -->
<!--          trophic_group = as.factor(trophic_group)) -->

<!-- write_csv(taxonomy_clean, glue("{dir_gdrive}/DATA_RAW/Scripps_Caselle_Fish_Data/clean_data/scripps_caselle_taxonomy_table.csv")) -->

<!-- ``` -->



